Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and it's audio-description

### 2020-07-06 paper/main.tex
draft of stability of contrasts results

% AO events
All of the original 19 categories of descriptive nouns except \texttt{++} were
used as events. Some categories that were similar but offered only a small
amount of counts were pooled resulting in eleven new categories (see Table
\ref{tab:ao-events}). Events that fall into one of the two setting-related
category but also into another category were treated as belonging to
setting-related category (\texttt{se\_new} or \texttt{se\_old}).
% null regressors
If a segment did not contain an event of a category, a null regressor was chosen for that segment.
\todo{wenn ich "null regressor" nehme, darf ich den ganzen Run, glaube ich, in
der 2nd level Analyse gar nicht benutzen? Hatte, glaube ich, Jeanette Mumford in
einem ihren Videos mal gesagt}
% modeling as boxcar function
Events were were modeled as boxcar function from onset to offset of each word.
% categories taken from movie cut annotation
Five additional categories were created from the annotation of movie cuts and
modeled as impulse events to capture variance of a possibly confounding change
of the soundscape after cuts, and to create contrasts of cross-modal negative control.
% nuissance regressors
Lastly, we used continuous bins of information about two auditory features
(left-right difference in volume and root mean square energy) that was averaged
across the length of every movie frame (\unit[40]{ms}) via Python script to
capture variance correlating with low-level perceptual processes.
% Reference to table
A short explanation and counts of the eleven speech-related event categories,
the five movie cut-related categories, and the two low-level confounds can be
found in Table \ref{tab:ao-events}.

@@

\begin{table*}[t]
    \caption{Contrasts of parameter estimates for the analysis of
        the audio-only stimulus (AO).
\texttt{all non-geo} = body, bodypart, fahead, object, sex\_f, sex\_m). Contrast
1-8 aim to isolate the PPA.
Contrast 9-13 serve as negative control at the moments of movie cuts
with possible changes of the audio tracks soundscape (see Table \ref{tab:av-contrasts}}

@@

\paragraph{second level (+ alignment)}
% single subjects (for Bland-Altman-Plots) 1st level
The GLM analysis that fitted each voxel's time course separately for each
subject was performed in functional space preserving the orientation of the EPI
images.
% two ways of co-registration
For the subsequent second level results, we co-registered the subjects in two ways.
% subject template (for Bland-Altman-Plot of unthresholded maps)
% \href{"https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/sub-01/bold3Tp2/brain.nii.gz"}{example})
On the one hand, subject-specific BOLD T1* time series were anatomically aligned
via linear transformation to a subject-specific, study-specific T1* template
that served as standard space.
% group template (for group and individual brain slices)
% https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/templates/grpbold3Tp2/brain.nii.gz"
On the other hand, time series were aligned via non-linear transformation to a
study-specific T2* group template.
% MNI152
This reference images was later co-registered to the MNI 152 template with an
affine transformation (12 degrees of freedom) to facilitate visualization and
identification of cortical structures,

\subsubsection{second level}
% model
The second level analyses which averaged contrast estimates over the eight
stimulus segments were carried out using a fixed effects model by forcing the
random effects variance to zero in FLAME (FMRIB's Local Analysis of Mixed
Effects; \citep{beckmann2003general, woolrich2004multilevel}.
% thresholding (Z>2.3 in subject-space; Z>3.4 in group space)
(Gaussianised T/F) statistic images were thresholded using clusters determined
by Z>3.4 and a (corrected) cluster significance threshold of p=.05
\citep{worsley2001statistical}.

\subsubsection{third level}
% model
The third level analysis which averaged contrast estimates over subjects were
carried out using FLAME stage 1 with automatic outlier detection
\citep{beckmann2003general, woolrich2004multilevel, woolrich2008robust}.
% thresholding
Z (Gaussianised T/F) statistic images were thresholded using clusters determined
by Z>3.4 and a (corrected) cluster significance threshold of p=.05
\citep{worsley2001statistical}.

% brain region identification
Brain regions associated with observed clusters were determined with the Juelich
Histological Atlas \citep{eickhoff2005toolbox, eickhoff2007assignment} and the
Harvard-Oxford Cortical Atlas \citep{desikan2006automated} provided by FSL.
% PPA masks
PPA ROI masks for individual subjects and a PPA group mask of individual PPAs overlapping were created from data provided by \citep{sengupta2016extension}.

@@

\subsection{stability contrasts}
See Figure \ref{fig:stability-slices}.
-> Tabelle machen

\begin{figure*} \centering
    \includegraphics[width=\linewidth]{figures/stability-slices}
    \caption{stability of contrasts}
    \label{fig:stability-slices}
\end{figure*}

@@

>>>>

% AO events
All of the original 19 categories of descriptive nouns except \texttt{++} were
used as events. Some categories that were similar but offered only a small
amount of counts were pooled resulting in eleven new categories (see Table
\ref{tab:ao-events}). Events that fall into one of the two setting-related
category but also into another category were treated as belonging to
setting-related category (\texttt{se\_new} or \texttt{se\_old}).
% null regressors
If a segment did not contain an event of a category, a null regressor was chosen
for that segment.  \todo{wenn ich "null regressor" nehme, darf ich den ganzen
    Run, glaube ich, in der 2nd level Analyse gar nicht benutzen? Hatte, glaube
    ich, Jeanette Mumford in einem ihren Videos mal gesagt}
% modeling as boxcar function
Events were were modeled as boxcar function from onset to offset of each word.
% categories taken from movie cut annotation
Five additional categories were created from the annotation of movie cuts and
modeled as impulse events to capture variance of a possibly confounding change
of the soundscape after cuts, and to create contrasts of cross-modal negative
control.
% nuissance regressors
Lastly, we used continuous bins of information about two auditory features
(left-right difference in volume and root mean square energy) that was averaged
across the length of every movie frame (\unit[40]{ms}) via Python script to
capture variance correlating with low-level perceptual processes.
% Reference to table
An explanation and counts of the eleven speech-related event categories,
the five movie cut-related categories, and the two low-level confounds can be
found in Table \ref{tab:ao-events}.

@@

\begin{table*}[t]
    \caption{Contrasts of parameter estimates for the analysis of
        the audio-only stimulus (AO).
\texttt{all non-geo} = body, bodypart, fahead, object, sex\_f, sex\_m).
Contrast
1-8 aim to isolate the PPA.
Contrasts 9-13 serve as negative control at the moments of movie cuts
with possible changes of the audio tracks soundscape (see Table
\ref{tab:av-contrasts}).}

@@

\paragraph{alignment etc.}
% single subjects (for Bland-Altman-Plots) 1st level
The GLM analysis that fitted each voxel's time course separately for each
subject was performed in functional space preserving the orientation of the EPI
images.
% two ways of co-registration
For the subsequent second level results, we co-registered the subjects in two
ways.
% subject template (for Bland-Altman-Plot of unthresholded maps)
% \href{"https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/sub-01/bold3Tp2/brain.nii.gz"}{example})
On the one hand, subject-specific BOLD T1* time series were anatomically aligned
via linear transformation to a subject-specific, study-specific T1* template
that served as standard space.
% group template (for group and individual brain slices)
% https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/templates/grpbold3Tp2/brain.nii.gz"
On the other hand, time series were aligned via non-linear transformation to a
study-specific T2* group template.
% MNI152
This reference images was later co-registered to the MNI 152 template with an
affine transformation (12 degrees of freedom) to facilitate visualization and
identification of cortical structures,

% second level
% model
The second level analyses which averaged contrast estimates over the eight
stimulus segments were carried out using a fixed effects model by forcing the
random effects variance to zero in FLAME (FMRIB's Local Analysis of Mixed
Effects; \citep{beckmann2003general, woolrich2004multilevel}.
% thresholding (Z>2.3 in subject-space; Z>3.4 in group space)
(Gaussianised T/F) statistic images were thresholded using clusters determined
by Z>3.4 and a (corrected) cluster significance threshold of p=.05
\citep{worsley2001statistical}.

% third level
% model
The third level analysis which averaged contrast estimates over subjects was
carried out using FLAME stage 1 with automatic outlier detection
\citep{beckmann2003general, woolrich2004multilevel, woolrich2008robust}.
% thresholding
Here again, Z (Gaussianised T/F) statistic images were thresholded using
clusters determined by Z>3.4 and a (corrected) cluster significance threshold of
p=.05 \citep{worsley2001statistical}.
% brain region identification
Brain regions associated with observed clusters were determined with the Juelich
Histological Atlas \citep{eickhoff2005toolbox, eickhoff2007assignment} and the
Harvard-Oxford Cortical Atlas \citep{desikan2006automated} provided by FSL.
% PPA masks
PPA ROI masks for individual subjects and a PPA group mask of individual PPAs overlapping were created from data provided by \citep{sengupta2016extension}.

@@

\todo[inline]{I consider tables of significant clusters for every contrast as
overkill. One contrast, the ``primary contrast'', appropriate.}

\subsection{stability contrasts}
The overlap of significant clusters of the 7 (well actually 8) contrast for the
audio-description, and 5 contrasts computed for the movie can be found in Figure
\ref{fig:stability-slices}.

% AO
\todo{alle noch einmal im einzelnen angucken; was ist mit COPE 8, der ist in der
Abb. nicht drin; zeigt (noch) einer keine sign. cluster?}
% PPA
Six of seven AO contrasts show significant bilateral clusters in anterior
regions of the group PPA overlap (which is temporal occipital fusiforim gyrus
regarding to co-registered Harvard-Oxford Cortical Structural Atlas).
% Precuneus = Retro Spenial Cortex ?
Six of seven contrasts show significant clusters in the ventral precuneus /
retrospenial cortex (RSC)

% AV
% PPA
All five AV contrasts yielded significant bilateral clusters in (temporal)
occipital, fusiform cortex showing congruency with the group overlap of
individual PPA ROIs.
% Lingual Gyrus
Homologous clusters of three contrasts extend further into lingual gyrus.
% RSC
Three contrasts show significant bilateral clusters in RSC.
% LOC
Four contrasts show signficant bilateral clusters in laterial occipital cortex

\begin{figure*} \centering
    \includegraphics[width=\linewidth]{figures/stability-slices}
    \caption{Stability of contrasts. Overlap of significant clusters (Z>3.4;
        p<.05, cluster corrected) of contrasts created to isolate the PPA. Blue:
        contrasts 1-7 (see Table \ref{tab:ao-contrasts} for the
    audio-description.}. Red: contrasts 1-5 (see Table \ref{tab:av-contrasts}
    for the audio-visual movie. Black: outline of overlapping individual PPA
    ROIs \citep{sengupta2016extension}.  \label{fig:stability-slices}
\end{figure*}

@@

\subsection{anterior (AO) vs. posterior (AV) PPA}
